Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-07-09 analysis/paper/sim_survey_paper.Rmd
Complete initial description of simulation

@@

The next step in the simulation is to distribute the abundance-at-age matrix simulated using the cohort model throughout a spatial field. Here, a grid of $s$ locations was generated with a resolution of $r$, a depth gradient, $S$ depth-based strata and $D$ divisions. The depth gradient was set-up to have a sigmoid shape with a depth range of $[d_{min}, d_{max}]$, shelf depth of $d_{shelf}$ and a shelf width of $w_{shelf}$. The simulated population is distributed through the grid by simulating spatial-temporal noise controled by a parabolic relationship with depth and covariance between ages, years and space

@@

Where $d_s$ is the depth in a specific cell of the grid, $\mu_d$ is the mean depth where abundance is typically highest and $\sigma_d$ controls the width or disperson of abundance around the mean. This helps simulate depth preferences of praticular fish. Residual noise $\xi_{a,y,s}$ is added to this depth relationship using a combination of Matérn covariance, to control the level of spatial aggregation, and the age-year covariance described in Cadigan [-@Cadigan2016], to control the level of similarity in distributions across ages and years. Spatial correlations was controled by a smoothing ($\lambda$) and scaling parameter ($\kappa$) [@Blangiardo2015] and correlation across ages and years was controled by $\varphi_{\xi, age}$ and $\varphi_{\xi, year}$, respectively. The overall variance of the process was controled by $\sigma_{\xi}^2$. In short, this formulation allows control of depth preferences, the level of spatial aggregation and the amount of age and year specific clustering. Note that $\eta_{a,y,s}$ is forced to sum to one in each year to ensure that the total population of each age for each year through the grid equals the number simulated by the cohort model. A more detailed description of the space-age-year covariance is included in Appendix 1.

The final step in the simulation is to conduct a stratified random survey over the age-year-space array generated using formula described above.

>>>>

## Simulate abundance

@@

## Simulate spatial distribution

The next step in the simulation is to distribute the abundance-at-age matrix simulated using the cohort model throughout a spatial field. Here, a grid of $s$ locations was generated with a resolution of $r$ and a depth gradient. The depth gradient was set-up to have a sigmoid shape with a depth range of $[d_{min}, d_{max}]$, shelf depth of $d_{shelf}$ and a shelf width of $w_{shelf}$. The simulated population is distributed through the grid by simulating spatial-temporal noise controled by a parabolic relationship with depth and covariance between ages, years and space

@@

Where $d_s$ is the depth in a specific cell of the grid, $\mu_d$ is the mean depth where abundance is typically highest and $\sigma_d$ controls the width or disperson of abundance around the mean. This helps simulate depth preferences of praticular fish. Residual noise $\xi_{a,y,s}$ is added to this depth relationship using a combination of Matérn covariance, to control the level of spatial aggregation, and the age-year covariance described in Cadigan [-@Cadigan2016], to control the level of similarity in distributions across ages and years. Spatial correlations was controled by a smoothing ($\lambda$) and scaling parameter ($\kappa$) [@Blangiardo2015] and correlation across ages and years was controled by $\varphi_{\xi, age}$ and $\varphi_{\xi, year}$, respectively. The overall variance of the process was controled by $\sigma_{\xi}^2$. In short, this formulation allows control of depth preferences, the level of spatial aggregation and the amount of age and year specific clustering. Note that $\eta_{a,y,s}$ is forced to sum to one in each year to ensure that the total population of each age for each year through the grid equals the number simulated by the cohort model. Also note that numbers were rounded such that a discrete number of fish are in each cell of the grid. A more detailed description of the space-age-year covariance is included in Appendix 1.

## Simulate survey

The final step in the simulation is to conduct a stratified random survey over the age-year-space array generated using formula described above. First, the grid is divided into $N_{div}$ divisions and $N_{strat}$ depth-based strata. The area of each strata is calculated and this is used to define the sets to allocate to each strata under a praticular set density, $D_{sets}$. The allocated number of cells are randomly selected in each strata and the number of fish caught in each set is calculated by applying binomial sampling of the fish in each sampled cell by the proportion of the area covered by the trawl and the catchability of each age:

$$n_{a,y,s} \sim Bin(N_{a,y,s}, \frac{A}{r^2} q_a )$$
Where $n_{a,y,s}$ is the number of fish sampled by a set, $A$ indicates the area covered by the trawl, $r$ is the resolution of the grid cells, and $q_a$ is the catchability coefficient of each age. Here, catchabilities were defined using a logistic curve controled by a steepness, $k$, and midpoint parameter, $x_0$. The lengths of the fish sampled by the set are then simulated using the original von Bertalanffy growth curve [@Cailliet2006]:

$$log(l) = log(l_{\infty} - (l_{\infty} - l_0) e^{-Ka}) + \varepsilon$$
Where $l_{\infty}$ is the mean asympotic lengths, $l_0$ is length at birth, $K$ is the growth rate parameter and the error is assumed to follow the normal distribution, $\varepsilon \sim N(0, \sigma_{l}^2)$. Depending on the number of fish caught, sub-sampling is then conducted. Specifically, a maximum number of lengths are measured per set, $M_{lengths}$, and a maximum number of ages, $M_{ages}$, are sampled per length group, $l_{group}$, per division.

## Simulation settings
